Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-13 manuscript/tables&figures.Rmd
worked on table 1
add draft model visualization figure
#71

Parentheses indicate that the prediction was supported by one but not all of the top full models (Table **5**). Dash symbols indicate that the response was not significant, or not represented in any of the top full models.
Asterisks indicate that the $Rt_{ARIMA}$ model yielded a different result: 
*different significance in $Rt_{ARIMA}$ model
**$Rt_{ARIMA}$ model had a significant trend in the opposite direction of the $Rt$ model (if significant) or the prediction (if no signficant trend in $Rt$ model).

@@

@@

>>>>

Parentheses indicate that the prediction was supported by one but not all of the top full models (Table **5**). Dash symbols indicate that the response was not significant/ not represented in any of the top full models.
Asterisks indicate that the $Rt_{ARIMA}$ model yielded a different result: 
*different significance in $Rt_{ARIMA}$ model
**$Rt_{ARIMA}$ model had a significant trend in the opposite direction of the $Rt$ model (if significant) or the prediction (if no signficant trend in $Rt$ model).

@@

**Figure 4. ...**

@@

![**Figure 4. Visualization of top models for all droughts combined and for each drought separately.** Model coefficients are given in Table S6. **THIS IS NOT YET CORRECT--CANOPY POSITION NEEDS TO BE CHANGED TO CATEGORICAL VARIABLE, AND THE POSITIVE HEIGHT EFFECT FOR 1999 IS ALSO WRONG (PROBABLY ARTIFACT OF CP). FINAL FIG WILL MATCH MODELS IN TABLE S6.** ](tables_figures/publication/regr_visuals.png){width=500px}
